Device Fingerprinting for User Authentication in Web Applications \titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2018-11-16 paper.tex
Capitalize title
Update paper.tex
Co-Authored-By: githubxxcc <xuchen727@hotmail.com>

\title{Device fingerprinting for user authentication in web applications
\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
%%%  \subtitle{[Extended Abstract]
%%% \titlenote{A full version of this paper is available as
%%% \textit{Author's Guide to Preparing ACM SIG Proceedings Using
%%% \LaTeX$2_\epsilon$\ and BibTeX} at
%%% \texttt{www.acm.org/eaddress.htm}}}

@@

The authentication algorithm introduces a degree of complexity whereby the similarity of two device fingerprints is evaluated based on a threshold level. This threshold level is customizable during registration (Figure \ref{fig:level}) and explained in the table below.

>>>>

\title{Device Fingerprinting for User Authentication in Web Applications
\titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}}
%%%  \subtitle{[Extended Abstract]
%%% \titlenote{A full version of this paper is available as
%%% \textit{Author's Guide to Preparing ACM SIG Proceedings Using
%%% \LaTeX$2_\epsilon$\ and BibTeX} at
%%% \texttt{www.acm.org/eaddress.htm}}}

@@

The authentication algorithm introduces a degree of complexity whereby the similarity of two device fingerprints is evaluated based on a threshold level. This threshold level is customizable during registration and the different levels are explained in Figure \ref{fig:level}.
